Contextuality and the Born rule in fuzzy quantum theories

### 2017-04-06 prop_letter.tex
prop_letter.tex Here and there...

Although considering IVPM is new for a quantum theory, people have
already defined classical IVPMs~\cite{JamisonLodwick2004}, which
are essentially the same as quantum IVPMs on a restricted mutually
commuting sub-event space~$\events'\subseteq\events$, where any
subset of $\events$ is called a sub-event space if it satisfies the
follow conditions. 
\begin{itemize}
\item $\mathbb{0}\in\events'$. 
\item $\mathbb{1}\in\events'$. 
\item For any projection $P\in\events'$, we have $\mathbb{1}-P\in\events'$. 
\item For a set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}\subseteq\events'$,
we have $\sum_{i=1}^{N}P_{i}\in\events'$. 
\end{itemize}
Quantum IVPM not only stems from classical IVPM but also generalizes
quantum real-valued probability measures. Consider the collection
of intervals are all singletons~$\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$,
and a function~$\iota_{\infty}:\left[0,1\right]\rightarrow\mathscr{I}_{\infty}$
defined by $\iota_{\infty}\left(x\right)=\left[x,x\right]$. Then,
given a quantum real value probability measure~$\mu:\events\rightarrow\left[0,1\right]$,
$\bar{\mu}(P)=\iota\left(\mu(P)\right)$ is a quantum IVPM, and vice
versa. In another word, when quantum IVPMs with $\mathscr{I}_{\infty}$
are just the same as quantum real-valued probability measures which
can fit Gleason's theorem.

However, quantum IVPMs certainly contains richer phenomena. For example,
we will show the Kochen-Specker theorem~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA}
is another limiting case when the collection of intervals are $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $,
where $\imposs=\left[0,0\right]$ and $\necess=\left[1,1\right]$,
in the next paragraph.

@@

Recall when providing infinity measurement resource, the quantum probability
measures are simply induced by the Born rule for $d\ge3$. If we increase
the measurement resource, i.e., pick finer intervals when constructing
IVPMs, it would be natural to ask whether quantum IVPMs would approach
the Born rule. In order to understand this question, it is instructive
to consider the 2-dimensional non-Born quantum probability measure~$\mu:\events\rightarrow[0,1]$
defined as follow:
\begin{equation}
\mu(P)=\begin{cases}
\mu_{\ket{\ps}}^{B}(P) & \textrm{, if }P=\proj{\ps}\textrm{ or }\proj{\ms}\textrm{ ;}\\
\mu_{\ket{0}}^{B}(P) & \textrm{, otherwise.}
\end{cases}
\end{equation}
Notice that $\mu$ is consistent with the Born rule partially, because
it is computed according to different states when applying on different
projectors. \newpage{}

>>>>

Although considering IVPM is new for a quantum theory, people have
already defined classical IVPMs~\cite{JamisonLodwick2004}, which
are essentially the same as quantum IVPMs on a restricted mutually
commuting sub-event space~$\events'\subseteq\events$, where any
subset of $\events$ is called a sub-event space if it satisfies the
follow conditions. 
\begin{itemize}
\item $\mathbb{0}\in\events'$. 
\item $\mathbb{1}\in\events'$. 
\item For any projection $P\in\events'$, we have $\mathbb{1}-P\in\events'$. 
\item For a set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}\subseteq\events'$,
we have $\sum_{i=1}^{N}P_{i}\in\events'$. 
\end{itemize}
Quantum IVPM not only stems from classical IVPM but also generalizes
quantum real-valued probability measures. Consider the collection
of intervals are all singletons~$\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$,
and a function~$\iota_{\infty}:\left[0,1\right]\rightarrow\mathscr{I}_{\infty}$
defined by $\iota_{\infty}\left(x\right)=\left[x,x\right]$. Then,
given a quantum real-valued probability measure~$\mu:\events\rightarrow\left[0,1\right]$,
$\bar{\mu}(P)=\iota\left(\mu(P)\right)$ is a quantum IVPM, and vice
versa. In another word, quantum IVPMs with $\mathscr{I}_{\infty}$
are just the same as quantum real-valued probability measures where
Gleason's theorem can apply.

$\mathscr{I}_{\infty}$ is one extreme case of quantum IVPM; another
extreme case happens when the collection of intervals are $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $,
where $\imposs=\left[0,0\right]$ and $\necess=\left[1,1\right]$.
This is the case where the Kochen-Specker theorem~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA}
can be applied and will be explained in the next paragraph.

@@

Recall when providing infinity measurement resource, the quantum probability
measures are simply induced by the Born rule for $d\ge3$. If we increase
the measurement resource, i.e., pick finer intervals, it is natural
to ask whether quantum IVPMs approach the Born rule. In order to understand
this question, it is instructive to consider the 2-dimensional non-Born
quantum probability measure~$\mu:\events\rightarrow[0,1]$ defined
as follow:
\begin{equation}
\mu_{0}(P)=\begin{cases}
\mu_{\ket{\ps}}^{B}(P) & \textrm{, if }P\in\events_{0}\textrm{ ;}\\
\mu_{\ket{0}}^{B}(P) & \textrm{, otherwis,}
\end{cases}
\end{equation}
where $\events_{0}=\left\{ \mathbb{0},\proj{\ps},\proj{\ms},\mathbb{1}\right\} $
is a sub-event space. In another word, $\mu_{0}$ is consistent with
the Born rule on every proper sub-event space, but not on the set
of all projectors.

Given a quantum IVPM~$\bar{\mu}$, the preceding idea motivates the
definition of \emph{core} relative to a sub-event space~$\events'$
as follow.
\begin{equation}
\mathrm{core}\left(\bar{\mu},\events'\right)=\set{\rho}{\forall P\in\events'.~\mu_{\rho}^{B}\left(P\right)\in\bar{\mu}\left(P\right)}\textrm{ .}
\end{equation}
Although the elements of a core are density matrices, we may just
use the state vectors for pure states if it is clear in the context.
For example, $\mathrm{core}\left(\iota_{\infty}\circ\mu_{0},\events_{0}\right)=\left\{ \ket{\ps}\right\} $,
where $\circ$ denote function composition.\newpage{}
